---
execute:
  eval: false
params:
    source_url: "https://connect.posit.cloud/ivelasq/content/0190c2c9-dd44-d440-0f97-f3b3bf073d0f"
# ERROR: Unknown option "--output-dir". Did you mean option "--no-render"?
# server: shiny
title: "My first Quarto dashboard"
format:
  dashboard:
    orientation: rows
---
+ https://bit.ly/quarto-dashboards



+ quarto serve "/Users/johngavin/docs_gh/hellow/inst/qmd/dashboard_ivelasq/shiny Add Interactive Components.qmd"
+ ERROR: inst/qmd/dashboard_ivelasq/shiny Add Interactive Components.qmd uses server: shiny so cannot be included in a website project (shiny documents require a backend server and so can't be published as static web content).


```{r}
#| context: setup
library(ggplot2)
```

## {.sidebar}

```{r}
selectInput(
    "variableChoice",
    "Choose a variable:",
    choices = names(mtcars)
  )
```

## Column

### Row

Here is my dashboard:

### Row

```{r}
#| title: "Plot 2"
plotOutput("variablePlot")
```

```{r}
#| context: server
output$variablePlot <- renderPlot({
  yVar <- mtcars[[input$variableChoice]]
  plot(mtcars$index, yVar)
})
```
