---
params:
    source_url: "https://www.kenkoonwong.com/blog/gemini/#minimal-reproducible-code"
title: "Untitled"
format: html
---


```{r}
library(tidyverse)
library(reticulate)

# install Python, using pyenv
install_python(
  # latest patch via python.org
  # 3.12.5 Aug 24
  version = "3.12:latest",
  list = FALSE,
  force = FALSE,
  optimized = TRUE
)

# 1: virtual env - a best practice.
# conda create -n gemini python=3.12
# ls ~/.virtualenvs/
# python3.12 -m venv ~/.virtualenvs/gemini
# source ~/.virtualenvs/gemini/bin/activate
# pip3 install google-generativeai langchain langchain-community pypdf python-dotenv
# manually installed python; manually get path
py_vers <- "/opt/homebrew/Caskroom/miniconda/base/envs/gemini/bin/python"
# 3.12.5 v 3.12.4?!
use_python(py_vers, required = TRUE)
py_config()


virtualenv_create(
  envname = "gemini",
  version = "3.12:latest"
)
use_condaenv("gemini", required = TRUE)
# /Users/johngavin/.virtualenvs/gemini/bin/python3.12
# use_miniconda(
#     condaenv = "gemini",
#     required = TRUE)
# use_virtualenv("gemini", required = TRUE))


py_install(c("google-generativeai", "langchain", "langchain-community", "pypdf", "python-dotenv"), pip = T, virtualenv = "gemini")

# Step 2: Use the virtual environment
# use_virtualenv("gemini")

# Step 3: Import installed modules
dotenv <- import("dotenv"
langchain_community <- import("langchain_community")
PyPDFLoader <- langchain_community$document_loaders$PyPDFLoader
langchain <- import("langchain")
PromptTemplate <- langchain$prompts$PromptTemplate
genai <- import("google.generativeai")
# genai <- import("google-generativeai")
# genai <- import("google_generativeai")

# Step 4: Load your API keys onto a .env file - see https://pypi.org/project/python-dotenv/
dotenv$load_dotenv(dotenv_path = ".env", verbose = TRUE)
```
```{r}
# Step 5: Load PDF of interest
fp <- file.path(
  "~/Downloads",
  "Profitable Day Trading Strategy For The U.S. Equity.pdf"
)
loader <- PyPDFLoader(fp)
documents <- loader$load()

# Step 6: Setup Gemini
genai$configure() # if you're skipping dotenv, insert your API key here```{r, eval = FALSE} # ----
llm <- genai$GenerativeModel(
  "gemini-1.5-flash",
  generation_config = genai$GenerationConfig(
    max_output_tokens = 2000L,
    temperature = 0
  )
)

# Step 7 (optional): Test
# FAIL Gemini API free tier is not available in your country.
llm$generate_content(contents = "hello") # you should see a return of text and tokens etc.

# Step 8: Prompt
prompt_text <- "
You are a question and answer assistant. Given the context below, answer the question.

Context: {text}

Question: {question}
"

prompt <- PromptTemplate(template = prompt_text, input_variables = list("text", "question"))

questions <- c(
  "What is the preferred treatment of CRE?",
  "What is the preferred treatment of ESBL-E?",
  "Can we use fosfomycin in ESBL Klebsiella?",
  "Can we use fosfomycin in ESBL Ecoli?",
  "What is the preferred treatment of stenotrophomonas?",
  "What is the preferred treatment of DTR Pseudomonas?",
  "Which organisms require two active agent when susceptibility is known?",
  "Can we use gentamicin in pseudomonas infection?",
  "Can we use tobramycin to treat pseudomonas infection?",
  "Why is there carbapenemase non-producing organism?",
  "Can we use oral antibiotics for any of these MDRO?",
  "What is the preferred treatment of MRSA?",
  "What is the preferred treatment of CRAB?",
  "Can fosofmycin be used for pyelonephritis?",
  "Is IV antibiotics better than oral antibiotics?"
)

content <- prompt$format(
  text = documents,
  question = questions
)

# Step 9: Generate Content / aka Langchain lingo == invoke
response <- llm$generate_content(contents = content)

# Step 10: Let's simulate a streaming response 🤪
print_keystrokes <- function(text) {
  for (char in strsplit(text, "")[[1]]) {
    cat(char) # Print the character
    Sys.sleep(0.005) # Optional delay for visual effect
  }
  cat("\n") # Add a newline at the end
}

print_keystrokes(response$text)

```
